---
title: "Revisions_1"
output: html_document
---

Import all necessary packages
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(vegan)
library(factoextra)

```


Biomass data import and wrangling.Taking mean of biomass at plot level
```{r}
df_biomass <- read.csv("data/rf_biomass.csv" ) %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  mutate(plot_id = str_remove(plant_id, pattern = "[0-9]-")) %>% 
  mutate(plot_id = str_remove(plot_id, pattern = "-[KP]"))


nw_biomass <- df_biomass %>% 
  group_by(plant_community, plot_id) %>% 
  summarize(biomass_mean = mean(biomass)) %>% 
  ungroup() %>% 
  mutate(patch_size = str_extract(plot_id, pattern = "[A-Z]"))

```


Nutrient data import and wrangling
```{r}
df_nut <- read.csv("data/soil_cn.csv") %>% 
  janitor::clean_names() %>% 
  mutate(cn = c_result/n_result) %>% 
  mutate(plot_id = str_extract(id, pattern = "[A-Z][0-9]+"))
```


Import Element data and wrangling
```{r}
ele_df <- read.csv( "data/elements.csv" ) %>% 
  janitor::clean_names() %>% 
  arrange(code) 

df_ele <- ele_df %>% 
  select(-c(code, patch_size, plant_community, sample))
```

DATA RE-ANLAYSIS



Biomass analysis. Plot level mean calculated.
patch included as fixed effect. Plot numbers are random variables.
```{r}
mod_biomass <- lmer(sqrt(biomass_mean) ~ plant_community*patch_size + (1|plot_id)  , data = nw_biomass)
lattice::qqmath(mod_biomass)
shapiro.test(resid(mod_biomass))
anova(mod_biomass)
hist(resid(mod_biomass))
```



Carbon analysis. 
patch included as fixed effect. Plot numbers are random variables.
```{r}
mod_carbon <- lmer(sqrt(c_result) ~ plant_community*patch_size + (1|plot_id)  , data = df_nut)
lattice::qqmath(mod_carbon)
shapiro.test(resid(mod_carbon))
anova(mod_carbon)
hist(resid(mod_carbon))
```



Nitrogen analysis. 
patch included as fixed effect. Plot numbers are random variables.
```{r}
mod_nitrogen <- lmer(sqrt(n_result) ~ plant_community*patch_size + (1|plot_id)   , data = df_nut)
lattice::qqmath(mod_nitrogen)
shapiro.test(resid(mod_nitrogen))
anova(mod_nitrogen)
hist(resid(mod_nitrogen))
```



Carbon/Nitrogen analysis. 
patch included as fixed effect. Plot numbers are random variables
```{r}
mod_cn <- lmer(cn ~ plant_community*patch_size + (1|plot_id), data = df_nut)
lattice::qqmath(mod_cn)
shapiro.test(resid(mod_cn))
anova(mod_cn)
hist(resid(mod_cn))
```



PCA of the elemental composition
```{r}
norm_ele <- vegan::decostand(df_ele, method = "normalize", MARGIN = 1)
pc <- prcomp(norm_ele)
summary(pc)$importance[,1:2]
var <- get_pca_var(pc)
var$contrib
fviz_contrib(pc, choice = "var", axes = 1, top = 10)

PC1 <- pc$x[,1]
PC2 <- pc$x[,2]

dist_eucc <- vegdist(norm_ele, method = "euclidean")

set.seed(11111)
adonis2(dist_eucc ~ ele_df$plant_community * ele_df$patch_size)
```

