---
title: "Revisions_1"
output: html_document
---

#Import all necessary packages
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(vegan)
library(factoextra)
library(FactoMineR)
library(ggsci)
library(patchwork)
library(ggpubr)

```


#Biomass data import and wrangling.Taking mean of biomass at plot level
```{r}
df_biomass <- read.csv("data/rf_biomass.csv" ) %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  mutate(plot_id = str_remove(plant_id, pattern = "[0-9]-")) %>% 
  mutate(plot_id = str_remove(plot_id, pattern = "-[KP]"))


nw_biomass <- df_biomass %>% 
  group_by(plant_community, plot_id) %>% 
  summarize(biomass_mean = mean(biomass)) %>% 
  ungroup() %>% 
  mutate(patch_size = str_extract(plot_id, pattern = "[A-Z]"))

```


#Nutrient data import and wrangling
```{r}
df_nut <- read.csv("data/soil_cn.csv") %>% 
  janitor::clean_names() %>% 
  mutate(cn = c_result/n_result) %>% 
  mutate(plot_id = str_extract(id, pattern = "[A-Z][0-9]+"))
```


#Import Element data and wrangling
```{r}
ele_df <- read.csv( "data/elements.csv" ) %>% 
  janitor::clean_names() %>% 
  arrange(code) 

df_ele <- ele_df %>% 
  select(-c(code, patch_size, plant_community, sample))
```

#*DATA RE-ANLAYSIS*



#Biomass analysis. Plot level mean calculated.
patch included as fixed effect. Plot numbers are random variables.
```{r}
mod_biomass <- lmer(sqrt(biomass_mean) ~ plant_community*patch_size + (1|plot_id)  , data = nw_biomass)
lattice::qqmath(mod_biomass)
shapiro.test(resid(mod_biomass))
anova(mod_biomass)
hist(resid(mod_biomass))
```



#Carbon analysis. 
patch included as fixed effect. Plot numbers are random variables.
```{r}
mod_carbon <- lmer(sqrt(c_result) ~ plant_community*patch_size + (1|plot_id)  , data = df_nut)
lattice::qqmath(mod_carbon)
shapiro.test(resid(mod_carbon))
anova(mod_carbon)
hist(resid(mod_carbon))
```



#Nitrogen analysis. 
patch included as fixed effect. Plot numbers are random variables.
```{r}
mod_nitrogen <- lmer(sqrt(n_result) ~ plant_community*patch_size + (1|plot_id)   , data = df_nut)
lattice::qqmath(mod_nitrogen)
shapiro.test(resid(mod_nitrogen))
anova(mod_nitrogen)
hist(resid(mod_nitrogen))
```



#Carbon/Nitrogen analysis. 
patch included as fixed effect. Plot numbers are random variables
```{r}
mod_cn <- lmer(cn ~ plant_community*patch_size + (1|plot_id), data = df_nut)
lattice::qqmath(mod_cn)
shapiro.test(resid(mod_cn))
anova(mod_cn)
hist(resid(mod_cn))
```



#PCA of the elemental composition
```{r}
norm_ele <- vegan::decostand(df_ele, method = "normalize", MARGIN = 1)
pc <- prcomp(norm_ele)
summary(pc)$importance[,1:2]
var <- get_pca_var(pc)
var$contrib
fviz_contrib(pc, choice = "var", axes = 1, top = 10)


PC1 <- pc$x[,1]
PC2 <- pc$x[,2]

dist_eucc <- vegdist(norm_ele, method = "euclidean")


```

#Plots
```{r}
biomass <- ggplot(df_biomass, aes(x = plant_community,y = sqrt(biomass), fill = plant_community )) +
  geom_violin(width= 0.5, alpha = 0.6,show.legend = F) +
  geom_boxplot(width = 0.25) +
  ylim(c(0,1.4))+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x =  element_blank(),
        axis.ticks.x = element_blank()) +
  ggeasy::easy_all_text_colour(colour = "black") +
  ggeasy::easy_all_text_size(size =14) +
  scale_fill_jama(name = "Knapweed", labels = c("Invaded", "Uninvaded")) +
  labs(x = NULL,
       y = expression(sqrt(Biomass ~(g)))) +
  geom_segment(aes(x = 1, xend = 2,
                   y = 1.3, yend = 1.3),
               lwd = 1) +
  annotate(geom = "text", x = 1.5, y = 1.35, label = "*", size = 10)

carbon <- ggplot(df_nut, aes(x = plant_community,y = sqrt(c_result), fill = plant_community )) +
  geom_violin(width= 0.5, alpha = 0.6, show.legend = F) +
  geom_boxplot(width = 0.25) +
  ylim(c(0,4))+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x =  element_blank(),
        axis.ticks.x = element_blank()) +
  ggeasy::easy_all_text_colour(colour = "black") +
  ggeasy::easy_all_text_size(size =14) +
  scale_fill_jama(name = "Knapweed", labels = c("Invaded", "Uninvaded")) +
  labs(x = NULL,
       y = expression(sqrt(Carbon ~("%")))) +
  geom_segment(aes(x = 1, xend = 2,
                   y = 3.5, yend = 3.5),
               lwd = 1) +
  annotate(geom = "text", x = 1.5, y = 3.6, label = "**", size = 10)

nitrogen <-  ggplot(df_nut, aes(x = plant_community,y = sqrt(n_result), fill = plant_community )) +
  geom_violin(width= 0.5, alpha = 0.6, show.legend = F) +
  geom_boxplot(width = 0.25) +
  ylim(c(0,1.5))+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x =  element_blank(),
        axis.ticks.x = element_blank()) +
  ggeasy::easy_all_text_colour(colour = "black") +
  ggeasy::easy_all_text_size(size =14) +
  scale_fill_jama(name = "Knapweed", labels = c("Invaded", "Uninvaded")) +
  labs(x = NULL,
       y = expression(sqrt(Nitrogen ~("%")))) +
  geom_segment(aes(x = 1, xend = 2,
                   y = 1.25, yend = 1.25),
               lwd = 1) +
  annotate(geom = "text", x = 1.5, y = 1.3, label = "*", size = 10)

carbon_nitrogen <- ggplot(df_nut, aes(x = plant_community,y = cn, fill = plant_community )) +
  geom_violin(width= 0.5, alpha = 0.6, show.legend = F) +
  geom_boxplot(width = 0.25) +
  ylim(c(0,15))+
  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.text.x =  element_blank(),
        axis.ticks.x = element_blank()) +
  ggeasy::easy_all_text_colour(colour = "black") +
  ggeasy::easy_all_text_size(size =14) +
  scale_fill_jama(name = "Knapweed", labels = c("Invaded", "Uninvaded")) +
  labs(x = NULL,
       y = expression(sqrt(Nitrogen ~("%")))) +
  geom_segment(aes(x = 1, xend = 2,
                   y = 12.5, yend = 12.5),
               lwd = 1) +
  annotate(geom = "text", x = 1.5, y = 13, label = "**", size = 10)


comb_plot <- (biomass + carbon) / (nitrogen + carbon_nitrogen  ) +
  plot_annotation(tag_levels = 'A', tag_prefix = "2") +
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')

comb_plot_new <- comb_plot & theme(axis.title.y =  element_text(size = 24),
                                   legend.text =  element_text(size = 20),
                                   legend.title = element_text(size = 20))

comb_plot_new

ggsave (comb_plot_new, filename = "comb_plot.jpg", path = "./plot_revision1", width = 12, height = 10, units = "in", dpi = 900)



```

#Correlations
```{r}

rf_biom <- read.csv("data/rf_biomass.csv") %>% 
  janitor::clean_names() %>% 
  mutate(id = str_remove(plant_id, "^[1-9]+-*")) %>% 
  drop_na() %>% 
  group_by(plant_community, id) %>% 
  summarise(bm = mean(biomass), .groups = "drop")%>% 
  mutate(id = str_remove(id, "-")) %>% 
  arrange(id)

cn_df <- read.csv("data/soil_cn.csv") %>% 
  janitor::clean_names() %>% 
  arrange(id) %>% 
  mutate(id = str_trim(id))

ele_df <- read.csv( "data/elements.csv" ) %>% 
  janitor::clean_names() %>% 
  arrange(code) 
 
df_ele <- ele_df %>% 
  select(-c(code, patch_size, plant_community, sample))

meta_ele <- ele_df %>% 
   rename(id = code) %>% 
  left_join(., rf_biom, by = "id") %>% 
  left_join(., cn_df, by = "id") %>% 
  rename(treatment = plant_community.x)

norm_ele <- vegan::decostand(df_ele, method = "normalize", MARGIN = 1)

pc <- prcomp(norm_ele)
summary(pc)$importance[,1:2]


PC1 <- pc$x[,1]
PC2 <- pc$x[,2]

plt_df <- data.frame(PC1, PC2,
                     meta_ele)

```

#correlation plot
```{r}
Corr_carbon_PC1 <-ggplot(plt_df, aes(x= PC1, y = c_result)) +
  geom_point(pch = 21, fill = "royalblue4", size = 4, alpha = 0.5) +
  geom_smooth(method = "lm", se = T, color = "black",  lwd = 1, linetype = 5) +
  stat_cor(method = "pearson", label.x = -0.1, label.y = 12, size = 5) +
  labs(y = "Carbon %",
       x = "PC axis 1") +
  theme_classic() +
  ggeasy::easy_all_text_size(size = 14) +
  ggeasy::easy_all_text_color("black") +
  ylim(c(0,13))
                             

Corr_nitrogen_PC1 <-ggplot(plt_df, aes(x= PC1, y = n_result)) +
  geom_point(pch = 21, fill = "royalblue4", size = 4, alpha = 0.5) +
  geom_smooth(method = "lm", se = T, color = "black",  lwd = 1, linetype = 5) +
  stat_cor(method = "pearson", label.x = -0.1, label.y = 1.35, size = 5) +
  labs(y = "Nitrogen %",
       x = "PC axis 1") +
  theme_classic() +
  ggeasy::easy_all_text_size(size = 14) +
  ggeasy::easy_all_text_color("black") +
  ylim(c(0,1.5))


Corr_bm_PC1 <-ggplot(plt_df, aes(x= PC1, y = bm)) +
  geom_point(pch = 21, fill = "royalblue4", size = 4, alpha = 0.5) +
  geom_smooth(method = "lm", se = T, color = "black", lwd = 1, linetype = 5) +
  stat_cor(method = "pearson", label.x = -0.1, label.y = 0.8, size = 5) +
  labs(y = "Biomass (g)",
       x = "PC axis 1") +
  theme_classic() +
  ggeasy::easy_all_text_size(size = 14)+
  ggeasy::easy_all_text_color("black")+
  ylim(c(0,0.85))

plt <- Corr_carbon_PC1 + Corr_nitrogen_PC1 + Corr_bm_PC1 + plot_annotation(tag_levels = 'A', tag_prefix = "4") & theme(axis.title = element_text(size = 20) )
plt
ggsave(plt, filename = "corr_plt.jpg", path = "./plot_revision1", width = 10, height = 3.25, units = "in", dpi = 800)
```


#PCA figure
```{r}
dist_eucc <- vegdist(norm_ele, method = "euclidean")

set.seed(11111)
adonis2(dist_eucc ~ ele_df$plant_community * ele_df$patch_size)

nutrient_dis <- ggplot(plt_df, aes(PC1, PC2, fill = treatment))+
  stat_ellipse(geom = "polygon", level = 0.95, alpha = 0.3, show.legend = F) +
  geom_point(pch= 21, size = 5) +
  scale_fill_jama(name ="Knapweed",
                  label = c("Invaded", "Uninvaded")) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        legend.position = c(0.173, 0.999),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6),
        legend.box.background = element_rect(color="black")) +
  labs(x = "Axis 1 (Variance 51.29 %)",
       y = "Axis 2 (Variance 35.87 %)")  +
  annotate("text", label = "Pseudo F = 4.77; p = 0.007", x = 0.1, y = -0.12, size = 5 ) +
  ggeasy::easy_all_text_colour(colour = "black") +
  ggeasy::easy_all_text_size(size =14)
nutrient_dis
  ggsave(nutrient_dis, filename = "nutrient_dis.jpg",path = "./plot_revision1", width = 8, height = 6, units = "in",dpi = 800)


```

